problem years

### 2024-08-13 src/problem_years.Rmd
legend

library(tidyverse)
library(rprojroot)
library(plm)
library(sf)
library(magick)
library(ggrepel)
library(scales)

@@

filename = paste(path.out, t, ".png", sep = "")
ggsave(filename, bg='#ffffff')
}

# legend
path.out <- paste0(path, "/outputs/lisa/corrected/LA/lisa_level_pc", n, "_la_legend.png") 
legend <- ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  # scale_fill_discrete_c4a_cat(name = "%", palette = "parks.charmonix",
  #                             na.translate = FALSE) +
  scale_fill_manual(values = palette_new, na.value="white", drop = F, name = NULL) +
  theme_minimal() +
  theme(legend.position="bottom")

legend <- cowplot::get_legend(for.legend)
plot(legend)  
ggsave(path.out, bg='#ffffff')
```

>>>>

library(tidyverse)
library(rprojroot)
library(plm)
library(sf)
library(magick)
library(ggrepel)
library(scales)
library(ggpubr)

@@

### lisa map legend
```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/LA/lisa_level_pc", n, "_la_legend.png") 
legend <- ggplot(data = la, aes(fill = quadr$median)) +
  geom_sf() +
  scale_fill_manual(values = palette_new, na.value="white", drop = F, name = NULL) +
  theme_minimal() +
  theme(legend.position="bottom",
        legend.margin=ggplot2::margin(c(1,1,1,1)))

legend <- cowplot::get_legend(for.legend)

leg <- as_ggplot(legend)
leg <- leg + theme(
  legend.margin=ggplot2::margin(c(0,0,0,0)))
ggsave(path.out, width = 5, height = 0.4, bg='#ffffff')
```
